NFC and burnout in teachers - A replication and extension study

### 2021-09-13 Manuscript/Manuscript.Rmd
updated all plots to have asterisks

@@

  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```

@@

@@

  fityears_plot <- semPaths(fityears, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 20, sizeMan2 = 7, shapeMan = "rectangle", label.norm = TRUE, # specify node properties
                       edge.label.cex = 1, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "#f0a543", negCol = "#5a99d1"
)
```

@@

@@

  fit2_plot <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edge.label.cex = 1, # size of the parameters
                        edge.label.color = "black", edge.label.bg = FALSE, # color and background of the parameters
                        posCol = "#f0a543", negCol = "#5a99d1" # color of arrows
  )
```

>>>>

  # create an array of standardized parameters and an array of significances

  fit_param <- fit_summ$PE$std.all[1:7]
  fit_sign <- fit_summ$PE$pvalue[1:7]

  # replace p-values with asterisks depending on significance level

  fit_sign <- ifelse(fit_sign < .001, "***", ifelse(fit_sign < .01, "**", ifelse(fit_sign < .05, "*", "")))

  # paste correlations and asterisks together

  fit_param <- paste(format(round(fit_param, digits = 2), nsmall = 2), fit_sign, sep = "")

@@

  fit_plot <- semPaths(fit, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition"),
                       layout = matrix(data = c(0,0,0,1,-1,1,-0.3,-1,0.3,0.3), nrow = 5, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edgeLabels = fit_param, # specify the edge labels with the asterisks as previously created
                       edge.label.cex = 1, esize = 2, # size specifications
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

  # create an array of standardized parameters and an array of significances

  fityears_param <- fityears_summ$PE$std.all[1:8]
  fityears_sign <- fityears_summ$PE$pvalue[1:8]

  # replace p-values with asterisks depending on significance level

  fityears_sign <- ifelse(fityears_sign < .001, "***", ifelse(fityears_sign < .01, "**", ifelse(fityears_sign < .05, "*", "")))

  # paste correlations and asterisks together

  fityears_param <- paste(format(round(fityears_param, digits = 2), nsmall = 2), fityears_sign, sep = "")

@@

  fityears_plot <- semPaths(fityears, what="std", # display the parameters on the arrows
                       nodeLabels = c("Self-Control", "Reappraisal", "Suppression", "Reduced\nPersonal Efficacy", "Need for Cognition", "Years spent\nteaching"),
                       layout = matrix(data = c(0,0,0,1,-1,-1,1,-0.3,-1,0.3,0.3,1), nrow = 6, ncol = 2), # manually set the node locations
                       sizeMan = 24, sizeMan2 = 7, shapeMan = "rectangle", label.scale = FALSE, # specify node properties
                       edge.label.cex = 1, esize = 2, # size specifications
                       edgeLabels = fityears_param, # specify the edge labels with the asterisks as previously created
                       fade = FALSE, # do not make insignificant associations invisible
                       residuals = FALSE, # do not plot residuals
                       exoCov = FALSE, # do not plot covariance between exogenous variables
                       edge.label.color = "black", posCol = "black", negCol = "black"
)
```

@@

  # create an array of standardized parameters and an array of significances

  fit2_param <- fit2_summ$PE$std.all[1:23]
  fit2_sign <- c(rep(1,16), fit2_summ$PE$pvalue[17:23])

  # replace p-values with asterisks depending on significance level

  fit2_sign <- ifelse(fit2_sign < .001, "***", ifelse(fit2_sign < .01, "**", ifelse(fit2_sign < .05, "*", "")))

  # paste correlations and asterisks together

  fit2_param <- paste(format(round(fit2_param, digits = 2), nsmall = 2), fit2_sign, sep = "")

@@

  fit2_plot <- semPaths(fit2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4","dth1","dth2","dth3","dtl1","dtl2","dtl3","drf1","drf2","drf3","ee","dp","rpe","NFC","DTH","DTL","DRF","MBI"),
                        layout = matrix(data = c(-1,-0.8,-0.6,-0.4,-0.8,-0.6,-0.4,-0.2,0,0.2,0.4,0.6,0.8,0.6,0.8,1,-0.8,-0.6,0,0.6,0.8,
                                                 -1,-1,-1,-1,1,1,1,1,1,1,1,1,1,-1,-1,-1,-0.5,0.5,0.5,0.5,-0.5),
                                        nrow = 21, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```
